Using traffic analysis to identify The Second Generation Onion Router

### 2011-06-13 ieee-conference-paper/paper.tex
Fix wording of last sentence in Tor vulnerabilities paragraph

When designing a system such as Tor, a number of trade-offs have to be made
between the strength of the security provided and the convenience and
performance of the system. The Tor designers consciously prioritized low
latency, usability and flexibility against security goals such as security
against end to end attacks \parencite[4]{Dingledine:2004p314}. These design
decisions mean that Tor is vulnerable to several kinds of attacks, some of them
expected and some not.

>>>>

When designing a system such as Tor, a number of trade-offs have to be made
between the strength of the security provided and the convenience and
performance of the system. Tor designers consciously prioritized low latency,
usability and flexibility against security goals such as security against end
to end attacks \parencite[4]{Dingledine:2004p314}. This means that by design,
Tor is vulnerable to a global passive adversary, however there are some attacks
that were not expected by the designers.
